Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-01 awipev-CO2.Rmd
clean up

### Traitement des variables

* temp_mix = temp 11m + temp_insitu_ctd_9m si trous.
* sal_mix = sal FB + sal_insitu_ctd_9m si trous.
* ph_s_sf_temp_mix: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
* ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* pco2_calc: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* Relation at / sal_mix 
* at_calc: calculé from sal_mix
* E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_mix (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
* phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)

### **FerryBox**

- **2020-03-13**: Salinity was filtered above 28 in d_all.rds file.
- **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.

@@

## Villefranche Server informations

@@

### Data processing

#### Script ny-alesund_cc.R which runs on awipev@awipev-co2.obs-vlfr.fr
* reads data from the AWI NRT database [Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736) 
* calibrates pCO2 data
* data cleaning:
  + Argo Global Range Test.
  + filter salinities above 28
  + filter temperatures above 10
  + filter seaFET Volt (outliers)
  + filter seaFET pH (outliers)
  + filter durafet (outliers)
* Quality flags
    + 1: good data
    + 3: impossible date and time test
    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
    + 6: failing the manufacturer range test (not used)
    + 7: failing the regional range test 
    + 12: failing the spike test (NAs from despike)
    + 13: failing the gradient test
    + 15: the instrument was not deployed or operated
    + 99: failing the final visual inspection of the data. 
* Despike using oce::despike with n=2, k=5761
* Files generated:
    + previous_NRT_data.rds: all NRT data without alteration from the beginning (2015)
    + all_nydata_minute.rds: all data after filtering and despike describe above (every minute)
    + all_nydata_hour.rds: hourly means of all data after filtering and despike describe above (every minute)
    + nydata_minute.rds: selected data after filtering and despike describe above (every minute). **Useful?**
    + nydata_hour.rds: selected hourly means of all data after filtering and despike describe above (every minute).  This is for further data processing.

#### Script awipev-co2.Rmd which runs locally
* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
* temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
* calibrate seafet pH
* calibrate durafet pH

@@

<!-- ```{r Graph pour proposal, echo=FALSE, message= FALSE, warning=FALSE} -->

<!-- p_sal <- ggplot() + -->
<!--          geom_point(data=d_all%>%filter(sal >28),aes(x=datetime, y=sal),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Salinity", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_temp_fb <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=temp_fb),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Temperature (in Ferrybox)", x="Time")+ ylim(c(-2.5, 9.5)) + -->
<!--         theme_bw() -->
<!--  p_pco2 <- ggplot() + -->
<!--          geom_point(data=d_all%>%filter(pco2_contros < 450),aes(x=datetime, y=pco2_contros),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Corrected pCO2", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_ta_raw <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=sal),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Salinity", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_sf <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=pHint_tot_sf),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Corrected seaFET pH", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_df <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=pH_durafet_),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Corrected seaFET pH", x="Time")+ -->
<!--         theme_bw() -->
<!-- ggsave("../fb_figures/Plots_proposal/p_sal.png", p_sal,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_temp_fb.png", p_temp_fb,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_pco2.png", p_pco2,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_sf.png", p_sf,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_df.png", p_df,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_ta.png", p_ta,width = 15, height = 5 ,units="cm") -->

<!--  # DURAFET  -->
<!-- durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, ph_s_dur_temp_fb) -->
<!-- durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime) -->
<!-- dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>% -->
<!--     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>% -->
<!--     dySeries("ph_s_dur_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
<!--     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>% -->
<!--     dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>%  -->
<!--     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>% -->
<!--     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>% -->
<!--     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>% -->
<!--     dyRangeSelector(height = 30)  -->
<!-- # SEAFET  -->
<!-- seafet_contros_xts <- dplyr::select(d_all, datetime, phINT,ph_s_sf_temp_mix) -->
<!-- seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime) -->
<!-- dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>% -->
<!--   dySeries("phINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>% -->
<!--   dySeries("ph_s_sf_temp_mix", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
<!--   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>% -->
<!--   dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%  -->
<!--   dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>% -->
<!--     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>% -->
<!--     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>% -->
<!--     dyRangeSelector(height = 30)  -->

>>>>

### **FerryBox**
- **2020-03-13**: Salinity was filtered above 28 in d_all.rds file.
- **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.

@@

## Data processing
#### Script ny-alesund_cc.R which runs on awipev@awipev-co2.obs-vlfr.fr
* reads data from the AWI NRT database [Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736) 
* calibrates pCO2 data
* data cleaning:
  + Argo Global Range Test.
  + filter salinities above 28
  + filter temperatures above 10
  + filter seaFET Volt (outliers)
  + filter seaFET pH (outliers)
  + filter durafet (outliers)
* Quality flags
    + 1: good data
    + 3: impossible date and time test
    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
    + 6: failing the manufacturer range test (not used)
    + 7: failing the regional range test 
    + 12: failing the spike test (NAs from despike)
    + 13: failing the gradient test
    + 15: the instrument was not deployed or operated
    + 99: failing the final visual inspection of the data. 
* Despike using oce::despike with n=2, k=5761
* Files generated:
    + previous_NRT_data.rds: all NRT data without alteration from the beginning (2015)
    + all_nydata_minute.rds: all data after filtering and despike describe above (every minute)
    + all_nydata_hour.rds: hourly means of all data after filtering and despike describe above (every minute)
    + nydata_minute.rds: selected data after filtering and despike describe above (every minute). **Useful?**
    + nydata_hour.rds: selected hourly means of all data after filtering and despike describe above (every minute).  This is for further data processing.

#### Script awipev-co2.Rmd which runs locally
* reads locally fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
* temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
* pco2_calc: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* calibrate seafet pH
    - ph_s_sf_temp_mix: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_mix (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
    - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* calibrate durafet pH
    - ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
* Relation at / sal_mix 
* at_calc: calculé from sal_mix
* saves locally d_all.rds which comprises all variables plus those generated in the script

### Villefranche Server informations

@@

@@
